---
title: "Main Analysis of Bovitz Data for Nexus"
author: "Reed Orchinik"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load packages and data
Load packages and set theme

```{r load, echo=FALSE, message=FALSE}
rm(list = ls())

library('dplyr')
library('stringr')
library('reshape2')
library('tidyr')
library('ggplot2')
library('readr')
library('bnlearn')
library('plotly')
library('fixest')
library('vtable')
library('brms')
library('BayesPostEst')
library('xtable')
library('lavaan')
library('blavaan')
library('tidySEM')
library('cluster')
library('factoextra')
library('nnet')
library('ggpubr')
library('ggcorrplot')
library('ggpattern')
library('knitr')
library('kableExtra')
library('ggh4x')
library('tidybayes')
library('ggridges')
library('tidyverse')

set.seed(1997)

theme_set(theme_light())
```

Load data, change to numeric, and do final cleaning
```{r data, echo=FALSE, message=FALSE}
df <- read.csv2('../data/final_clean.csv', sep = ",") %>%
  filter(drop == FALSE) %>%
  mutate(across(c(prior_sci_always_E_yes, prior_sci_always_E_no, prior_sci_unbiased,
                  prior_cc_occur_adj, prior_sci_unbiased_adj, prior_sci_skill_adj,
                  ends_with("_b0"), ends_with("_b1")), as.numeric))

table_path = "../tables/nexus"
figure_path = "../figures/nexus"

#Offset for plots
pd <- position_dodge(2)
```

# Main analyses
Create long version of dataframe where each row is an observation for a participant at a consensus level
```{r ind_cons, echo=FALSE, message=FALSE}
ind_cons <- df %>%
  #Pivot longer to get to ID-consensus observation
  pivot_longer(
    cols = starts_with("P_cc_given_cons"),
    names_to = "Consensus Level",
    names_prefix = "P_cc_given_cons",
    values_to = c("belief")
  ) %>%
  group_by("Consensus Level" = as.numeric(`Consensus Level`),
           ID = as.character(ID),
           Party) %>%
  summarise(belief = mean(belief))

#Same for all non-climate variables
namelist <- c("pro_bias", "anti_bias", "pro_skill", "anti_skill")
for(name in namelist){
  temp <- df %>%
    pivot_longer(
      cols = starts_with(sprintf("P_%s_given_cons", name)),
      names_to = "Consensus Level",
      names_prefix = sprintf("P_%s_given_cons", name),
      values_to = "var"
    ) %>%
    group_by("Consensus Level" = as.numeric(`Consensus Level`),
             ID = as.character(ID)) %>%
    summarise(var = mean(var))
  
  ind_cons <- left_join(ind_cons, temp)
  names(ind_cons)[names(ind_cons) == "var"] <- name
}

#Join in priors
ind_cons <- df %>%
  mutate(ID = as.character(ID)) %>%
  select(ID, prior_sci_unbiased, prior_sci_skill_adj,
         prior_cc_occur, prior_consensus_num, condition) %>%
  right_join(., ind_cons, by = "ID")
```

## Control group analyses
### Main regressions
Baseline regressions that appear in Table S2 and posterior probabilities of positive effects
```{r}
#Climate regression of belief on consensus and random intercept and slope
belief_m1_bayes <- ind_cons %>%
  filter(condition == "control") %>%
  mutate(consensus = `Consensus Level`) %>%
  brm(belief ~ consensus + (1 + consensus | ID),
      data = .,
      cores = 4,
      chains = 4)

#Get distribution of individual-level random effects and find probability of positive draw
distr_belief_ranef <- belief_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(ind_slope = b_consensus + r_ID) %>%
  group_by(ID) %>%
  summarise(mean = mean(ind_slope)) %>%
  ungroup() %>%
  summarise(prob_pos = mean(mean > 0))

#Same for pro-skill
pro_skill_m1_bayes <- ind_cons %>%
  filter(condition == "control") %>%
  mutate(consensus = `Consensus Level`) %>%
  brm(pro_skill ~ consensus + (1 + consensus | ID),
      data = .,
      cores = 4,
      chains = 4)

distr_pro_skill_ranef <- pro_skill_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(ind_slope = b_consensus + r_ID) %>%
  group_by(ID) %>%
  summarise(mean = mean(ind_slope)) %>%
  ungroup() %>%
  summarise(prob_pos = mean(mean > 0))

#pro-bias
pro_bias_m1_bayes <- ind_cons %>%
  filter(condition == "control") %>%
  mutate(consensus = `Consensus Level`) %>%
  brm(pro_bias ~ consensus + (1 + consensus | ID),
      data = .,
      cores = 4,
      chains = 4)

distr_pro_bias_ranef <- pro_bias_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(ind_slope = b_consensus + r_ID) %>%
  group_by(ID) %>%
  summarise(mean = mean(ind_slope)) %>%
  ungroup() %>%
  summarise(prob_pos = mean(mean > 0))

#anti-skill
anti_skill_m1_bayes <- ind_cons %>%
  filter(condition == "control") %>%
  mutate(consensus = `Consensus Level`) %>%
  brm(anti_skill ~ consensus + (1 + consensus | ID),
      data = .,
      cores = 4,
      chains = 4)

distr_anti_skill_ranef <- anti_skill_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(ind_slope = b_consensus + r_ID) %>%
  group_by(ID) %>%
  summarise(mean = mean(ind_slope)) %>%
  ungroup() %>%
  summarise(prob_pos = mean(mean > 0))

#anti-bias
anti_bias_m1_bayes <- ind_cons %>%
  filter(condition == "control") %>%
  mutate(consensus = `Consensus Level`) %>%
  brm(anti_bias ~ consensus + (1 + consensus | ID),
      data = .,
      cores = 4,
      chains = 4)

distr_anti_bias_ranef <- anti_bias_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(ind_slope = b_consensus + r_ID) %>%
  group_by(ID) %>%
  summarise(mean = mean(ind_slope)) %>%
  ungroup() %>%
  summarise(prob_pos = mean(mean > 0))
```

### Figure 1
Climate belief curves by consensus level, faceted by party without average
```{r, echo=FALSE, message=FALSE}
plot <- ind_cons %>%
  mutate('_Climate' = belief) %>%
  rename(ProConsensus_Bias = pro_bias,
         AntiConsensus_Bias = anti_bias,
         ProConsensus_Skill = pro_skill,
         AntiConsensus_Skill = anti_skill) %>%
  pivot_longer(
    cols = c("_Climate", "ProConsensus_Bias",
             "AntiConsensus_Bias", "ProConsensus_Skill", "AntiConsensus_Skill"),
    names_to = c("type", "measure"),
    names_pattern = "(.*)_(.*)"
  ) %>%
  dplyr::group_by(consensus = `Consensus Level`,
                  type,
                  measure,
                  Party = case_when(Party == "Dem" ~ "Democrat",
                                    Party == "Ind" ~ "Independent",
                                    Party == "Rep" ~ "Republican")) %>%
  dplyr::summarise(mean = mean(value, na.rm = TRUE),
                CI = 1.96*sd(value, na.rm = TRUE)/sqrt(n())) %>%
  ggplot(aes(x = consensus)) +
  geom_point(aes(y = mean, color = Party), position = pd) +
  # geom_point(aes(y = value, color = Party), position = pd, alpha = 0.005) +
  geom_line(aes(y = mean, color = Party), position = pd) +
  # geom_line(aes(y = value, color = Party, group = ID), position = pd, alpha = 0.01) +
  geom_errorbar(aes(ymin = mean - CI, ymax = mean + CI, color = Party),
                position = pd, alpha = 0.5) +
  ylab("Belief") +
  xlab("Consensus Level") +
  scale_x_continuous(breaks = c(50, 75, 100)) +
  scale_color_manual(values=c("#0000FF", "#006633", "#CC0000")) +
  scale_fill_manual(values=c("#0000FF", "#006633", "#CC0000")) +
  facet_wrap2(~factor(measure, levels = c("Climate", "Skill", "Bias")) +
                      factor(type, levels = c("", "ProConsensus", "AntiConsensus"),
                             labels = c("", "Pro-Consensus", "Anti-Consensus")),
              nrow = 1,
              strip = strip_nested(bleed = TRUE,
                                   background_x = list(NULL, NULL, NULL,
                                                       element_rect(fill = "grey90"),
                                                       element_rect(fill = "grey90"),
                                                       element_rect(fill = "grey90"),
                                                       element_rect(fill = "grey90"),
                                                       element_rect(fill = "grey90")),
                                   text_x = list(element_text(size = 15),
                                                 element_text(size = 15),
                                                 element_text(size = 15), NULL,
                                                 element_text(color = "black"),
                                                 element_text(color = "black"),
                                                 element_text(color = "black"),
                                                 element_text(color = "black")))) +
  theme(legend.position = "bottom",
        axis.title.x = element_text(size = 15),
        axis.text = element_text(size = 10),
        axis.title.y = element_text(size = 15),
        legend.text = element_text(size = 12),
        legend.title = element_text(size = 15),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank())

print(plot)
pdf(file = sprintf("%s/belief_curves_bovitz.pdf", figure_path), height = 6, width = 8)
print(plot)
dev.off()
```

### SEM 
Within-subject SEM
```{r SEM, echo=FALSE, message=FALSE, warning=FALSE}
model <- '
    level: within
        ProSkill ~ a1*Consensus
        AntiSkill ~ b1*Consensus
        ProBias ~ c1*Consensus
        AntiBias ~ d1*Consensus
        Climate ~ e1*Consensus + e2*ProSkill + e3*ProBias + e4*AntiSkill + e5*AntiBias
    level: between
        ProSkill ~ 1 + age + male + white + college + dem
        AntiSkill ~ 1 + age + male + white + college + dem
        ProBias ~ 1 + age + male + white + college + dem
        AntiBias ~ 1 + age + male + white + college + dem
        Climate ~ 1 + age + male + white + college + dem
    direct_effect := e1
    indirect_effect := (a1*e2) + (b1*e3) + (c1*e4) + (d1*e5)
    skill_path := a1*e2
    total_effect := e1 + (a1*e2) + (b1*e3) + (c1*e4) + (d1*e5)
'

bsem <- ind_cons %>%
  filter(condition == "control") %>%
  group_by(ID) %>%
  rename(consensus = `Consensus Level`) %>%
  arrange(consensus) %>%
  mutate(Climate = belief,
         ProSkill = pro_skill,
         ProBias = pro_bias,
         AntiSkill = anti_skill,
         AntiBias = anti_bias,
         Consensus = consensus) %>%
  left_join(., df %>%
              group_by(ID = as.character(ID)) %>%
              summarise(age = as.numeric(age),
                        male = as.numeric(gender == 1),
                        white = as.numeric(race == 4),
                        college = as.numeric(edu %in% c(5, 6)),
                        dem = as.numeric(Party == "Dem")),
            by = "ID") %>%
  bsem(model, data=., burnin = 1000, sample = 1000, n.chains = 4, bcontrol = list(cores = 4), cluster = "ID")

bsem_CIs <- data.frame(standardizedPosterior(bsem)) %>%
  select(ProSkill.Consensus:Climate.AntiBias, contains("effect")) %>%
  summarise(across(everything(), list(mean = mean, LB = ~quantile(.x, 0.025), UB = ~quantile(.x, 0.975))))

prop_indirect <- data.frame(standardizedPosterior(bsem)) %>%
  rename(direct_effect = starts_with("direct_effect"),
         indirect_effect = starts_with("indirect_effect"),
         total_effect = starts_with("total_effect"),
         skill_path = starts_with("skill_path")) %>%
  mutate(prop_indirect = indirect_effect/total_effect,
         indirect_direct_ratio = indirect_effect/direct_effect,
         prop_skill = skill_path/direct_effect) %>%
  summarise(across(c(prop_indirect:prop_skill),
                   list(mean = mean, LB = ~quantile(.x, 0.025), UB = ~quantile(.x, 0.975))))
```

#### Heterogeneity in updating ####
Create dataframe of belief curves using the random-effects from the previous Bayesian models
```{r}
belief_slopes <- belief_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(belief_slope = r_ID) %>%
  group_by(ID) %>%
  summarise(belief_slope_mean = mean(belief_slope),
            belief_slope_sd = sd(belief_slope))

pro_skill_slopes <- pro_skill_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(proskill_slope = r_ID) %>%
  group_by(ID) %>%
  summarise(proskill_slope_mean = mean(proskill_slope),
            proskill_slope_sd = sd(proskill_slope))

anti_skill_slopes <- anti_skill_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(antiskill_slope = r_ID) %>%
  group_by(ID) %>%
  summarise(antiskill_slope_mean = mean(antiskill_slope),
            antiskill_slope_sd = sd(antiskill_slope))

pro_bias_slopes <- pro_bias_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(probias_slope = r_ID) %>%
  group_by(ID) %>%
  summarise(probias_slope_mean = mean(probias_slope),
            probias_slope_sd = sd(probias_slope))

anti_bias_slopes <- anti_bias_m1_bayes %>%
  spread_draws(b_consensus, r_ID[ID,term]) %>%
  filter(term == "consensus") %>%
  mutate(antibias_slope = r_ID) %>%
  group_by(ID) %>%
  summarise(antibias_slope_mean = mean(antibias_slope),
            antibias_slope_sd = sd(antibias_slope))

slopes_df <- belief_slopes %>%
  left_join(., pro_skill_slopes) %>%
  left_join(., anti_skill_slopes) %>%
  left_join(., pro_bias_slopes) %>%
  left_join(., anti_bias_slopes) %>%
  left_join(., df)
```

Describe heterogeneity in one-step updating at aggregate level
```{r}
het <- ind_cons %>%
  group_by(ID = as.numeric(ID)) %>%
  rename(consensus = `Consensus Level`) %>%
  left_join(., (df %>%
                  select(ID, age, gender, edu, income, politics, uni.science.trust) %>%
                  mutate(across(everything(), ~as.numeric(.x))))) %>%
  mutate(male = gender == 1) %>%
  mutate(across(c("belief", "pro_skill", "anti_skill", "pro_bias", "anti_bias"),
                ~ (.x - lag(.x)))) %>%
  group_by(consensus) %>%
  summarise(mean = mean(belief),
            sd = sd(belief),
            pos = mean(belief > 0))
```

Function to compute LOO R^2
```{r}
bayes_R2_res <- function(fit) {
  y <- rstanarm::get_y(fit)
  ypred <- rstanarm::posterior_epred(fit)
  if (family(fit)$family == "binomial" && NCOL(y) == 2) {
    trials <- rowSums(y)
    y <- y[, 1]
    ypred <- ypred %*% diag(trials)
  }
  e <- -1 * sweep(ypred, 2, y)
  var_ypred <- apply(ypred, 1, var)
  var_e <- apply(e, 1, var)
  var_ypred / (var_ypred + var_e)
}
```

Predict heterogeneity in updates
```{r}
belief_update_demos_bayes <- ind_cons %>%
  group_by(ID = as.numeric(ID)) %>%
  rename(consensus = `Consensus Level`) %>%
  left_join(., (df %>%
                  select(ID, age, gender, edu, income, politics, 
                         uni.science.trust, race) %>%
                  mutate(across(everything(), ~as.numeric(.x))))) %>%
  mutate(age = as.numeric(age),
         female = as.numeric(gender == 2),
         college = as.numeric(edu == 5 | edu == 6),
         white = as.numeric(race == 4)) %>%
  mutate(across(c("belief", "pro_skill", "anti_skill", "pro_bias", "anti_bias"),
                ~ (.x - lag(.x)))) %>%
  filter(condition == "control") %>%
  na.omit() %>%
  brm(belief ~ Party + age + female + college + income + white + politics + uni.science.trust + (1 | ID) +
        (1 + Party + age + female + college + income + white + politics + uni.science.trust | consensus),
      data = .,
      control = list(adapt_delta = 0.99,
                     max_treedepth = 15),
      cores = 4,
      chains = 4)

median(bayes_R2_res(belief_update_demos_bayes))

belief_update_bayes <- ind_cons %>%
  filter(condition == "control") %>%
  group_by(ID) %>%
  rename(consensus = `Consensus Level`) %>%
  mutate(across(c("belief", "pro_skill", "anti_skill", "pro_bias", "anti_bias"),
                ~ (.x - lag(.x)))) %>%
  ungroup() %>%
  mutate(across(c("pro_skill", "anti_skill", "pro_bias", "anti_bias"), ~ scale(.x))) %>%
  brm(belief ~ pro_skill + anti_skill + pro_bias + anti_bias +
        (1 | ID) +
        (1 + pro_skill + anti_skill + pro_bias + anti_bias | consensus),
      data = .,
      control = list(adapt_delta = 0.999,
                     max_treedepth = 15),
      cores = 4,
      chains = 4)

median(bayes_R2_res(belief_update_bayes))

belief_update_bayes_priors <- ind_cons %>%
  filter(condition == "control") %>%
  group_by(ID) %>%
  rename(consensus = `Consensus Level`) %>%
  mutate(across(c("belief", "pro_skill", "anti_skill", "pro_bias", "anti_bias"),
                ~ (.x - lag(.x)))) %>%
  ungroup() %>%
  mutate(across(c("prior_cc_occur", "prior_consensus_num", "prior_sci_unbiased", "prior_sci_skill_adj"), ~ scale(.x))) %>%
  brm(belief ~ prior_cc_occur + prior_consensus_num +
        prior_sci_unbiased + prior_sci_skill_adj + (1 | ID) +
        (1 + prior_cc_occur + prior_consensus_num +
        prior_sci_unbiased + prior_sci_skill_adj | consensus),
      data = .,
      control = list(adapt_delta = 0.999,
                     max_treedepth = 15),
      cores = 4,
      chains = 4)

median(bayes_R2_res(belief_update_bayes_priors))
```

Same for backfires
```{r}
backfire_demos_bayes <- ind_cons %>%
  group_by(ID = as.numeric(ID)) %>%
  rename(consensus = `Consensus Level`)  %>%
  left_join(., (df %>%
                  select(ID, age, gender, edu, income, politics, uni.science.trust, race) %>%
                  mutate(across(everything(), ~as.numeric(.x))))) %>%
  mutate(age = as.numeric(age),
         female = as.numeric(gender == 2),
         college = as.numeric(edu == 5 | edu == 6),
         white = as.numeric(race == 4)) %>%
  mutate(across(c("belief", "pro_skill", "anti_skill", "pro_bias", "anti_bias"),
                ~ (.x - lag(.x))),
         backfire = belief < 0) %>%
  filter(condition == "control") %>%
  brm(backfire ~ Party + age + female + college + income + white + politics + uni.science.trust + (1 | ID) +
        (1 + Party + age + female + college + income + white + politics + uni.science.trust | consensus),
      data = .,
      family = bernoulli(link = "logit"),
      control = list(adapt_delta = 0.999,
                     max_treedepth = 15),
      cores = 4,
      chains = 4)

backfire_demos_bayes <- ind_cons %>%
  group_by(ID = as.numeric(ID)) %>%
  rename(consensus = `Consensus Level`)  %>%
  left_join(., (df %>%
                  select(ID, age, gender, edu, income, politics, uni.science.trust, race) %>%
                  mutate(across(everything(), ~as.numeric(.x))))) %>%
  mutate(age = as.numeric(age),
         female = as.numeric(gender == 2),
         college = as.numeric(edu == 5 | edu == 6),
         white = as.numeric(race == 4)) %>%
  mutate(across(c("belief", "pro_skill", "anti_skill", "pro_bias", "anti_bias"),
                ~ (.x - lag(.x))),
         backfire = belief < 0) %>%
  filter(condition == "control") %>%
  brm(backfire ~ Party + age + female + college + income + white + factor(politics) + uni.science.trust + (1 | ID) +
        (1 + Party + age + female + college + income + white + factor(politics) + uni.science.trust | consensus),
      data = .,
      family = bernoulli(link = "logit"),
      control = list(adapt_delta = 0.999,
                     max_treedepth = 15),
      cores = 4,
      chains = 4)

median(bayes_R2_res(backfire_demos_bayes))

backfire_bayes <- ind_cons %>%
  filter(condition == "control") %>%
  group_by(ID) %>%
  rename(consensus = `Consensus Level`) %>%
  mutate(across(c("belief", "pro_skill", "anti_skill", "pro_bias", "anti_bias"),
                ~ (.x - lag(.x))),
         backfire = belief < 0) %>%
  ungroup() %>%
  mutate(across(c("pro_skill", "anti_skill", "pro_bias", "anti_bias"), ~ scale(.x))) %>%
  brm(backfire ~ pro_skill + anti_skill + pro_bias + anti_bias + (1 | ID) +
        (1 + pro_skill + anti_skill + pro_bias + anti_bias | consensus),
      data = .,
      family = bernoulli(link = "logit"),
      control = list(adapt_delta = 0.999,
                     max_treedepth = 15),
      cores = 4,
      chains = 4)

median(bayes_R2_res(backfire_bayes))

backfire_bayes_priors <- ind_cons %>%
  filter(condition == "control") %>%
  group_by(ID) %>%
  rename(consensus = `Consensus Level`) %>%
  mutate(across(c("belief", "pro_skill", "anti_skill", "pro_bias", "anti_bias"),
                ~ (.x - lag(.x))),
         backfire = belief < 0) %>%
  ungroup() %>%
  mutate(across(c("prior_cc_occur", "prior_consensus_num", "prior_sci_unbiased", "prior_sci_skill_adj"), ~ scale(.x))) %>%
  brm(backfire ~ prior_cc_occur + prior_consensus_num +
        prior_sci_unbiased + prior_sci_skill_adj + (1 | ID) +
        (1 + prior_cc_occur + prior_consensus_num +
        prior_sci_unbiased + prior_sci_skill_adj | consensus),
      data = .,
      family = bernoulli(link = "logit"),
      control = list(adapt_delta = 0.999,
                     max_treedepth = 15),
      cores = 4,
      chains = 4)

median(bayes_R2_res(backfire_bayes_priors))
```

Show plot predicting heterogeneity in updates
```{r}
belief_update_draws <- belief_update_bayes %>%
  spread_draws(b_pro_skill, b_anti_skill, b_pro_bias, b_anti_bias)

backfire_draws <- backfire_bayes %>%
  spread_draws(b_pro_skill, b_anti_skill, b_pro_bias, b_anti_bias)

plot <- data.frame(belief_update_draws) %>%
  mutate(model = "Beliefs",
         Outcome = "OneStep Update") %>%
  bind_rows(data.frame(backfire_draws) %>%
              mutate(model = "Beliefs",
                     Outcome = "Backfire")) %>%
  pivot_longer(
    cols = c(b_pro_skill, b_anti_skill, b_pro_bias, b_anti_bias),
    names_to = "variable",
    names_pattern = "b_(.*)"
  ) %>%
  mutate(Variable = factor(case_when(grepl("pro_skill", variable) ~ "Pro-Consensus \nSkill",
                              grepl("anti_skill", variable) ~ "Anti-Consensus \nSkill",
                              grepl("pro_bias", variable) ~ "Pro-Consensus \nBias",
                              grepl("anti_bias", variable) ~ "Anti-Consensus \nBias"),
                           levels = c("Anti-Consensus \nBias", "Pro-Consensus \nBias",
                             "Anti-Consensus \nSkill", "Pro-Consensus \nSkill"))) %>%
  group_by(model,
           Outcome,
           Variable) %>%
  summarise(mean = mean(value),
            Q90 = quantile(value, 0.9),
            Q10 = quantile(value, 0.1),
            Q2.5 = quantile(value, 0.025),
            Q97.5 = quantile(value, 0.975)) %>%
  filter(model == "Beliefs") %>%
  ggplot(aes(x = Variable)) +
  geom_errorbar(aes(ymin = Q10, ymax = Q90, color = Variable),
                linewidth = 2, width = 0, position = position_dodge(1)) +
  geom_errorbar(aes(ymin = Q2.5, ymax = Q97.5, color = Variable),
                width = 0, position = position_dodge(1)) +
  geom_point(aes(y = mean, fill = Variable), position = position_dodge(1),
             size = 3, shape = 23, color = "black") +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed") +
  ylab("Predicted Relationship with Climate Belief") +
  xlab("") +
  coord_flip() +
  theme(text = element_text(size = 20),
        legend.position = "None") +
  facet_wrap(~Outcome, scales = "free_x")

print(plot)
pdf(file = sprintf("%s/het_updates.pdf", figure_path), height = 6, width = 8)
print(plot)
dev.off()
```

# Treatment Effects
Coefficient plot for average effect on each variable
```{r TE_plots, echo=FALSE, message=FALSE}
climate_exp_bayes <- ind_cons %>%
  mutate(consensus = `Consensus Level` - 50) %>%
  ungroup() %>%
  mutate(z_consensus = scale(as.numeric(consensus))) %>%
  brm(formula = belief ~ relevel(factor(condition), ref = "control") +
        (1 + consensus | ID),
      data = .,
      chains = 4,
      cores = 4)

climate_draws <- climate_exp_bayes %>%
  spread_draws(b_relevelfactorconditionrefEQcontroltrust, b_relevelfactorconditionrefEQcontrolskill)

mean(climate_draws$b_relevelfactorconditionrefEQcontroltrust > 0)
mean(climate_draws$b_relevelfactorconditionrefEQcontrolskill > 0)

pro_skill_exp_bayes <- ind_cons %>%
  mutate(consensus = `Consensus Level` - 50) %>%
  ungroup() %>%
  mutate(z_consensus = scale(as.numeric(consensus))) %>%
  brm(formula = pro_skill ~ relevel(factor(condition), ref = "control") + consensus +
        (1 + consensus | ID),
      data = .,
      chains = 4,
      cores = 4)

pro_skill_draws <- pro_skill_exp_bayes %>%
  spread_draws(b_relevelfactorconditionrefEQcontroltrust, b_relevelfactorconditionrefEQcontrolskill)

mean(pro_skill_draws$b_relevelfactorconditionrefEQcontroltrust > 0)
mean(pro_skill_draws$b_relevelfactorconditionrefEQcontrolskill > 0)

pro_bias_exp_bayes <- ind_cons %>%
  mutate(consensus = `Consensus Level` - 50) %>%
  ungroup() %>%
  mutate(z_consensus = scale(as.numeric(consensus))) %>%
  brm(formula = pro_bias ~ relevel(factor(condition), ref = "control") + consensus +
        (1 + consensus | ID),
      data = .,
      chains = 4,
      cores = 4)

pro_bias_draws <- pro_bias_exp_bayes %>%
  spread_draws(b_relevelfactorconditionrefEQcontroltrust, b_relevelfactorconditionrefEQcontrolskill)

mean(pro_bias_draws$b_relevelfactorconditionrefEQcontroltrust > 0)
mean(pro_bias_draws$b_relevelfactorconditionrefEQcontrolskill > 0)

anti_skill_exp_bayes <- ind_cons %>%
  mutate(consensus = `Consensus Level` - 50) %>%
  ungroup() %>%
  mutate(z_consensus = scale(as.numeric(consensus))) %>%
  brm(formula = anti_skill ~ relevel(factor(condition), ref = "control") + consensus +
        (1 + consensus | ID),
      data = .,
      chains = 4,
      cores = 4)

anti_skill_draws <- anti_skill_exp_bayes %>%
  spread_draws(b_relevelfactorconditionrefEQcontroltrust, b_relevelfactorconditionrefEQcontrolskill)

mean(anti_skill_draws$b_relevelfactorconditionrefEQcontroltrust < 0)
mean(anti_skill_draws$b_relevelfactorconditionrefEQcontrolskill < 0)

anti_bias_exp_bayes <- ind_cons %>%
  mutate(consensus = `Consensus Level` - 50) %>%
  ungroup() %>%
  mutate(z_consensus = scale(as.numeric(consensus))) %>%
  brm(formula = anti_bias ~ relevel(factor(condition), ref = "control") + consensus +
        (1 + consensus | ID),
      data = .,
      chains = 4,
      cores = 4)

anti_bias_draws <- anti_bias_exp_bayes %>%
  spread_draws(b_relevelfactorconditionrefEQcontroltrust, b_relevelfactorconditionrefEQcontrolskill)

mean(anti_bias_draws$b_relevelfactorconditionrefEQcontroltrust > 0)
mean(anti_bias_draws$b_relevelfactorconditionrefEQcontrolskill > 0)

plot <- climate_exp_bayes %>%
  spread_draws(b_relevelfactorconditionrefEQcontrolskill, b_relevelfactorconditionrefEQcontroltrust) %>%
  mutate(outcome = "belief") %>%
  rbind(., (pro_skill_exp_bayes %>%
              spread_draws(b_relevelfactorconditionrefEQcontrolskill, b_relevelfactorconditionrefEQcontroltrust) %>%
              mutate(outcome = "pro_skill"))) %>%
  rbind(., (pro_bias_exp_bayes %>%
              spread_draws(b_relevelfactorconditionrefEQcontrolskill, b_relevelfactorconditionrefEQcontroltrust) %>%
              mutate(outcome = "pro_bias"))) %>%
  rbind(., (anti_skill_exp_bayes %>%
              spread_draws(b_relevelfactorconditionrefEQcontrolskill, b_relevelfactorconditionrefEQcontroltrust) %>%
              mutate(outcome = "anti_skill"))) %>%
  rbind(., (anti_bias_exp_bayes %>%
              spread_draws(b_relevelfactorconditionrefEQcontrolskill, b_relevelfactorconditionrefEQcontroltrust) %>%
              mutate(outcome = "anti_bias"))) %>%
  rename(skill_TE = b_relevelfactorconditionrefEQcontrolskill,
         trust_TE = b_relevelfactorconditionrefEQcontroltrust) %>%
  pivot_longer(
    cols = c("skill_TE", "trust_TE"),
    values_to = "TE",
    names_to = "Condition",
    names_pattern = "(.*)_TE"
  ) %>%
  mutate(Outcome = factor(case_when(outcome == "belief" ~ "Climate \n Belief",
                             outcome == "pro_skill" ~ "Pro-Consensus \n Scientist Skill",
                             outcome == "pro_bias" ~ "Pro-Consensus \n Scientist Bias",
                             outcome == "anti_skill" ~ "Anti-Consensus \n Scientist Skill",
                             outcome == "anti_bias" ~ "Anti-Consensus \n Scientist Bias"),
                          levels = c("Anti-Consensus \n Scientist Bias", "Pro-Consensus \n Scientist Bias",
                                     "Anti-Consensus \n Scientist Skill", "Pro-Consensus \n Scientist Skill", "Climate \n Belief"))) %>%
  group_by(Condition,
           Outcome) %>%
  summarise(mean = mean(TE, na.rm = TRUE),
            UB = quantile(TE, probs = c(0.9)),
            LB = quantile(TE, probs = c(0.1)),
            UUB = quantile(TE, probs = c(0.975)),
            LLB = quantile(TE, probs = c(0.025))) %>%
  ggplot(aes(x = Outcome)) +
  geom_errorbar(aes(ymin = LB, ymax = UB, color = Condition),
                linewidth = 2, width = 0, position = position_dodge(1)) +
  geom_errorbar(aes(ymin = LLB, ymax = UUB, color = Condition),
                width = 0, position = position_dodge(1)) +
  geom_point(aes(y = mean, fill = Condition), position = position_dodge(1),
             size = 3, shape = 23, color = "black") +
  ylab("Treatment Effect") +
  xlab("") +
  geom_hline(yintercept = 0, color = "black", linetype = "dashed") +
  scale_color_manual(name = "Condition",
                     labels = c("History", "Institutions"),
                     values = c("#56B4E9", "#CC79A7"),
                     guide = guide_legend(reverse = TRUE)) +
  scale_fill_manual(name = "Condition",
                    labels = c("History", "Institutions"),
                    values = c("#56B4E9", "#CC79A7"),
                    guide = guide_legend(reverse = TRUE)) +
  coord_flip() + 
  theme(text = element_text(size = 20))

print(plot)
pdf(file = sprintf("%s/TE_coefplot.pdf", figure_path), width = 9, height = 6)
print(plot)
dev.off()
```